Untitled

### 2022-01-17 Main_Figures/Figure3_b.Rmd
Some figures for presentation at ebd

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27}

@@

theme_ms <- function(base_size=14, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
     theme(text=element_text(color="black"),
           axis.title=element_text( size = rel(2)),
           axis.text=element_text(size = rel(1.8), color = "black"),
           legend.title=element_text(face="bold",size=rel(2)),
           legend.text=element_text(size=rel(1.4)),
           legend.background=element_rect(fill="transparent"),
           legend.key.size = unit(1.8, 'lines'),
           panel.border=element_rect(color="black",size=2.4),
           panel.grid.minor.x =element_blank(),
           panel.grid.minor.y= element_blank(),
           panel.grid.major= element_blank(),
           plot.title = element_text(hjust = 0.5,size=rel(2.75),face="bold"),
           plot.subtitle = element_text(face="bold",size=rel(2.5))
     ))
}

@@

pp1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__), group=guild, colour=guild)) + geom_point(data = dat_analysis,
aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("Interaction")+ xlab("")+
  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids"))+ ggtitle("PC1", subtitle = "A")+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

@@

pp2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__), group=guild, colour=guild)) + geom_point(data = dat_analysis,
aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("")+ xlab("")+
  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids"))+ ggtitle("PC2", subtitle = "B") + scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

@@

combined <- pp1 + pp2 + pp3 + p1 + p2 + p3 & theme(legend.position = "bottom")
combined + plot_layout(guides = "collect",ncol = 3)

setwd("~/R_Projects/Reproductive Traits")

saveRDS(p1,"Main_Figures/figure_3_1.rds")
saveRDS(p2,"Main_Figures/figure_3_2.rds")
saveRDS(p3,"Main_Figures/figure_3_3.rds")
saveRDS(pp1,"Main_Figures/figure_3_4.rds")
saveRDS(pp2,"Main_Figures/figure_3_5.rds")
saveRDS(pp3,"Main_Figures/figure_3_6.rds")

>>>>

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=14}

@@

theme_ms <- function(base_size=14, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
     theme(text=element_text(color="black"),
           axis.title=element_text( size = rel(2.2)),
           axis.text=element_text(size = rel(2), color = "black"),
           legend.title=element_text(face="bold",size=rel(2)),
           legend.text=element_text(size=rel(1.4)),
           legend.background=element_rect(fill="transparent"),
           legend.key.size = unit(1.8, 'lines'),
           panel.border=element_rect(color="black",size=2.4),
           panel.grid.minor.x =element_blank(),
           panel.grid.minor.y= element_blank(),
           panel.grid.major= element_blank(),
           plot.title = element_text(hjust = 0.5,size=rel(2.75),face="bold"),
           plot.subtitle = element_text(face="bold",size=rel(2.5))
     ))
}

@@

pp1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__), group=guild, colour=guild)) + geom_point(data = dat_analysis,
aes(x = -PC1, y = Interaction),size = 2.8, alpha=0.4) + geom_line(size=1.8)  + ylab("Interaction")+ xlab("")+
  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids"))+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

@@

pp2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__), group=guild, colour=guild)) + geom_point(data = dat_analysis,
aes(x = -PC2, y = Interaction),size = 2.8, alpha=0.4) + geom_line(size=1.8)  + ylab("Interaction")+ xlab("")+
  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids"))+ scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

@@

pp2 + theme(legend.position = "bottom")

#combined <- pp1 + pp2 + pp3 + p1 + p2 + p3 & theme(legend.position = "bottom")
#combined + plot_layout(guides = "collect",ncol = 3)
